---
title: "Simple document"
author: "Diego Licona"
date: 2026-09-17
output: github_document
---

I'm an R Markdown document! 

# Section 0: libraries

```{r echo = F}
library(tidyverse)
```

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100) #this samples from a normal distribution
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Section 3: a tibble

```{r}

# Command + Option + I to create a new code chunk

plot_df =
  tibble(
    x = rnorm(1000, sd = 0.5),
    y = 1 + 2 * x + rnorm(1000)
  )

head(plot_df)
```


# Section 4: plots

```{r}

ggplot(plot_df, aes(x = x)) + geom_histogram()

ggplot(plot_df, aes(x = x, y = y)) + geom_point()

```

# Section 5: Learning Assessment 2

Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE?

```{r}
set.seed(0)

la_df = tibble(
  num_var = rnorm(n = 500, mean = 1),
  log_var = num_var > 0,
  abs_var = abs(num_var)
  
)

ggplot(la_df, aes(x = abs_var)) + geom_histogram()
```

The median is `r round(median(pull(la_df, num_var)), 2)`


# Section 7: Learning Assessment 3

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.

* The median is: r round(median(pull))


